CommonMind Consortium: DLPFC

### 2020-09-16 combined_analysis/combine_all_DLPFC.Rmd
bug fixes

data.frame(pi1 = 1 - qvalue(df_meta.inter_sex.disease[[coef]]$P)$pi0,
          `# DE` = sum(df_meta.inter_sex.disease[[coef]]$adj.P.Val < 0.05),
          check.names=FALSE ) %>% mutate_if(is.numeric, format, digits=3) %>% kable(caption="pi1 for SCZ:Sex meta-analysis") %>% kable_styling(full_width=FALSE)
```

>>>>

data.frame(pi1 = 1 - qvalue(df_meta.inter_sex.disease[[coef]]$P)$pi0,
          `# DE` = sum(df_meta.inter_sex.disease[[coef]]$adj.P.Val < 0.05),
          `# DE @ 10%` = sum(df_meta.inter_sex.disease[[coef]]$adj.P.Val < 0.1),
          check.names=FALSE ) %>% mutate_if(is.numeric, format, digits=3) %>% kable(caption="pi1 for SCZ:Sex meta-analysis") %>% kable_styling(full_width=FALSE)
```
